Testing specification of baseline models

### 2023-03-08 analysis/analysis_spec_tests.Rmd
Fix error in save of bic table
Change code for spec tests
Use svyglm models and report marginal probs for racial groups across model types

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE)
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
load(here("analysis","output","acs.RData"))
```

@@

I will judge model fit by the BIC statistic. I wil not consider survey design effects here for speed of computation.

```{r models-year-grade}
model_add_cat <- glm(below_exp_grade~as.factor(year)+current_grade+state, 
                     data=acs, family=binomial)
model_add_cont <- glm(below_exp_grade~I(year-2010)+current_grade+state, 
                     data=acs, family=binomial)
model_inter_cat <- glm(below_exp_grade~as.factor(year)*current_grade+state, 
                     data=acs, family=binomial)
model_inter_cont <- glm(below_exp_grade~I(year-2010)*current_grade+state, 
                     data=acs, family=binomial)
model_inter_state <- glm(below_exp_grade~I(year-2010)*current_grade+
                            I(year-2010)*state, 
                     data=acs, family=binomial)

bic_scores <- sapply(list("categorical, additive"=model_add_cat,
                          "categorical, interaction"=model_inter_cat, 
                          "continuous, additive"=model_add_cont, 
                          "continuous, interaction"=model_inter_cont,
                          "continous, interaction + state*year continuous interaction"=model_inter_state),
                     BIC) %>%
    enframe("model","BIC")

@@

save(bic_scores, save=here("analysis","output","bic_spec_tests.RData"))
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE, warning=FALSE, message=FALSE)
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
load(here("analysis","output","acs.RData"))
```

@@

I will judge model fit by the BIC statistic.

```{r models-year-grade}
acs_design <- acs %>%
  as_survey_design(ids = cluster, weights = perwt)
model0 <- svyglm(below_exp_grade~race, design=acs_design, family=binomial)
model_add_cat <- svyglm(below_exp_grade~as.factor(year)+current_grade+state+race, 
                     design=acs_design, family=binomial)
model_add_cont <- svyglm(below_exp_grade~I(year-2010)+current_grade+state+race, 
                     design=acs_design, family=binomial)
model_inter_cat <- svyglm(below_exp_grade~as.factor(year)*current_grade+state+race, 
                     design=acs_design, family=binomial)
model_inter_cont <- svyglm(below_exp_grade~I(year-2010)*current_grade+state+race, 
                     design=acs_design, family=binomial)
model_inter_state <- svyglm(below_exp_grade~I(year-2010)*current_grade+
                            I(year-2010)*state+race, 
                     design=acs_design, family=binomial)
```

```{r bic-scores}
bic_scores <- sapply(list("just race"=model0,
                          "categorical, additive"=model_add_cat,
                          "categorical, interaction"=model_inter_cat, 
                          "continuous, additive"=model_add_cont,
                          "continuous, interaction"=model_inter_cont,
                          "continous, interaction + state*year continuous interaction"=model_inter_state),
                     function(x) {
                       as.numeric(BIC(x, maximal=x)["BIC"])
                     }) %>%
    enframe("model","BIC")

@@

save(bic_scores, file=here("analysis","output","bic_spec_tests.RData"))
```

@@

Now lets take a look at how much the marginal probabilities of CBEG by race varies across model specifications.

```{r marg-fit-table}
marg_prob_alt <- list(model0, model_add_cat, model_add_cont, model_inter_cat, 
                  model_inter_cont, model_inter_state) |>
  map_dfc(function(x) {
    marg(x, "race", type="levels")[[1]]$Margin
  })

marg_prob_alt <- bind_cols(levels(acs$race), marg_prob_alt) |>
  rename(race=...1, baseline=...2, year_dummy=...3, year_linear=...4,
         year_dummy_interact=...5, year_linear_interact=...6, year_grade_state=...7)

marg_prob_alt |>
  gt() |>
  fmt_percent(2:7, decimals = 3) |>
  cols_label(race="Race", baseline="No Covariates", year_dummy="Year treated as dummy", 
             year_linear="Year treated as linear", year_dummy_interact="Year (dummy) x Grade",
             year_linear_interact="Year (linear) x Grade", 
             year_grade_stat="Year (linear) x Grade and State") |>
  tab_source_note("*Notes*: All models except no covariate case include dummies for current grade and state") |>
  tab_spanner("Sensitivity tests on calendar year x grade coding", 3:7)

save(marg_prob_alt, file=here("analysis","output","marg_prob_alt.RData"))
```

The answer is barely any. The only difference is the baseline model which makes sense because we are adding controls, but the difference between the model specifications is only visible out to the fifth decimal place on the proportions.

```{r time-end}
timestamp()
```
